---
title: "Example CREEDS API Usages Walk-Through"
author: "Zichen Wang"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load required packages

```{r, message=FALSE}
library(httr)
library(jsonlite)
library(Biobase)
library(GEOquery)
library(limma)
```

```{r}
BASE_URL <- 'http://amp.pharm.mssm.edu/CREEDS/'
```

## 1. Search signatures using text

```{r}
r <- GET(paste0(BASE_URL, 'search'), query=list(q ='breast cancer'))
response <- fromJSON(httr::content(r, 'text'))
print(r$status_code)
```

`response` is an R `data.frame`, have a look at the search result

```{r}
head(response)
```

## 2. Query the signature database using up/down gene sets to find similar/opposite signatures

Get vectors of up and down genes to query against the CREEDS database:

```{r}
## Get some up and down gene lists 
up_genes <- c('KIAA0907','KDM5A','CDC25A','EGR1','GADD45B','RELB','TERF2IP','SMNDC1','TICAM1','NFKB2','RGS2','NCOA3','ICAM1','TEX10','CNOT4','ARID4B','CLPX','CHIC2','CXCL2','FBXO11','MTF2','CDK2','DNTTIP2','GADD45A','GOLT1B','POLR2K','NFKBIE','GABPB1','ECD','PHKG2','RAD9A','NET1','KIAA0753','EZH2','NRAS','ATP6V0B','CDK7','CCNH','SENP6','TIPARP','FOS','ARPP19','TFAP2A','KDM5B','NPC1','TP53BP2','NUSAP1')
dn_genes <- c('SCCPDH','KIF20A','FZD7','USP22','PIP4K2B','CRYZ','GNB5','EIF4EBP1','PHGDH','RRAGA','SLC25A46','RPA1','HADH','DAG1','RPIA','P4HA2','MACF1','TMEM97','MPZL1','PSMG1','PLK1','SLC37A4','GLRX','CBR3','PRSS23','NUDCD3','CDC20','KIAA0528','NIPSNAP1','TRAM2','STUB1','DERA','MTHFD2','BLVRA','IARS2','LIPA','PGM1','CNDP2','BNIP3','CTSL1','CDC25B','HSPA8','EPRS','PAX8','SACM1L','HOXA5','TLE1','PYGL','TUBB6','LOXL1')
payload = list(
  up_genes = up_genes,
  dn_genes = dn_genes,
  direction= 'similar'
  )
```

POST the input gene sets to the API and load the response to R `data.frame`
```{r}
r <- POST(paste0(BASE_URL, 'search'), body=payload, encode='json')
print(r$status_code)
response <- fromJSON(httr::content(r, 'text'))
```

Have a look at the search result
```{r}
head(response)
```

3. Retrieve a signature using `id`
```{r}
r <- GET(paste0(BASE_URL, 'api'), query=list(id= response[1, 'id']))
sig <- fromJSON(httr::content(r, 'text'))
```

`sig` is a `list` with the following keys:
```{r}
names(sig)
```

